---
title: "Serving Spouses Program"
author: "Victoria Kincaid"
date: "3/21/2022"
output: html_document
---

Context: Our Serving Spouses program in a newer program from within Client Services. Through the Serving Spouses Program, new data will be collected for the purpose of better understanding our spouse clients and the unique employment challenges they face. This new data that will be collected by the Transition Specialists during Initial Assessments and will give HHUSA the power to analyze and improve the way the organization interacts with military spouse clients. With the ability to track and pull a range of reports, HHUSA can better understand its spouse clients by analyzing employment trends and identifying opportunities to better help spouse clients obtain meaningful employment.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(lubridate)
library(parsedate)
library(gridExtra)
library(knitr)
library(DT)
library(scales)
library(plyr)

EmployerProfile <- readxl::read_xlsx("D:/School Schtuff/Current Semester/Spring 2022/BAS 270/Data/EPO_Teradata_Employer_Profile_Creation_Report.xlsx")
SeekerProfile <- readxl::read_xlsx("D:/School Schtuff/Current Semester/Spring 2022/BAS 270/Data/EPO_Teradata_Job Seeker_Profile_Creation_Report.xlsx")
JobBoardSales <- readxl::read_xlsx("D:/School Schtuff/Current Semester/Spring 2022/BAS 270/Data/EPO_Teradata_Job_Board_Sales_Report.xlsx")

Feedback <- read.csv("D:/School Schtuff/Current Semester/Spring 2022/BAS 270/Data/Feedback__c.csv")
Campaign <- read.csv("D:/School Schtuff/Current Semester/Spring 2022/BAS 270/Data/Campaign.csv")
EmailHistoryContact <- read.csv("D:/School Schtuff/Current Semester/Spring 2022/BAS 270/Data/vr__VR_Email_History_Contact__c.csv")

SF2018Activities <- read.csv("D:/School Schtuff/Current Semester/Spring 2022/BAS 270/Data/SalesForce_2018Activities.csv")
SFAcct <- read.csv("D:/School Schtuff/Current Semester/Spring 2022/BAS 270/Data/SalesForce_Account.csv")
SFCase <- read.csv("D:/School Schtuff/Current Semester/Spring 2022/BAS 270/Data/SalesForce_Case.csv")
SFContact <- read.csv("D:/School Schtuff/Current Semester/Spring 2022/BAS 270/Data/SF_Contact.csv")
SFHI <- read.csv("D:/School Schtuff/Current Semester/Spring 2022/BAS 270/Data/SalesForce_Hire_Information__c.csv")
SFOpportunity <- read.csv("D:/School Schtuff/Current Semester/Spring 2022/BAS 270/Data/SalesForce_Opportunity.csv")
SFRecordType <- read.csv("D:/School Schtuff/Current Semester/Spring 2022/BAS 270/Data/SalesForce_RecordType.csv")
```

Q: What is the average amount in days that a military spouse spends in the HHUSA program? 

```{r}
Hire_Contact_Join <- left_join(SFContact, SFHI, by = c("Id" = "Client_Name__c"))
NarrowedHCJ <- Hire_Contact_Join[,c(1,50,57,69,256,265,300,321,388,401)]


###important!!!************************************************************
# which( colnames(Hire_Contact_Join) == "Federal_Hire__c.x" )
# grep("MyTrak", colnames(Hire_Contact_Join)) #jajaja
# Hire_Contact_Join$Dat_Initial_Assessment_was_Completed__c
# #

strptime(NarrowedHCJ$Date_Turned_Black__c, format = "%Y-%m-%d")
strptime(NarrowedHCJ$Date_turned_grey__c, format = "%m/%d/%Y")
strptime(NarrowedHCJ$Dat_Initial_Assessment_was_Completed__c, format = "%m/%d/%Y")
strptime(NarrowedHCJ$Confirmed_Hired_Date__c.y, format = "%Y-%m-%d")

NarrowedHCJ <- NarrowedHCJ %>% mutate(Dat_Initial_Assessment_was_Completed__c = mdy(Dat_Initial_Assessment_was_Completed__c))
NarrowedHCJ <- NarrowedHCJ %>% mutate(Confirmed_Hired_Date__c.y = ymd(Confirmed_Hired_Date__c.y))
NarrowedHCJ <- NarrowedHCJ %>% mutate(Date_Turned_Black__c = ymd(Date_Turned_Black__c))
NarrowedHCJ <- NarrowedHCJ %>% mutate(Date_turned_grey__c = mdy(Date_turned_grey__c))



NarrowedHCJ["Days_in_Program"] <- NA

for (i in 1:nrow(NarrowedHCJ)){
  if (NarrowedHCJ[i,"Active_Color__c"] == "Black") {
    NarrowedHCJ[i,"Days_in_Program"] <- difftime(NarrowedHCJ[i, "Date_Turned_Black__c"] , NarrowedHCJ[i,"Dat_Initial_Assessment_was_Completed__c"], units="days")
  }
  else if (NarrowedHCJ[i,"Active_Color__c"] == "Grey") {
    NarrowedHCJ[i,"Days_in_Program"] <- difftime(NarrowedHCJ[i, "Date_turned_grey__c"] , NarrowedHCJ[i,"Dat_Initial_Assessment_was_Completed__c"], units="days")
  }
  else if (NarrowedHCJ[i,"Active_Color__c"] == "Blue") {
    NarrowedHCJ[i,"Days_in_Program"] <- difftime(NarrowedHCJ[i, "Confirmed_Hired_Date__c.y"] , NarrowedHCJ[i,"Dat_Initial_Assessment_was_Completed__c"], units="DevelopmentAndEmployerPartnership.Rmdays")
  }
  else if (NarrowedHCJ[i,"Active_Color__c"] == "Green" | NarrowedHCJ[i,"Active_Color__c"] == "Purple" | NarrowedHCJ[i,"Active_Color__c"] =="Red") {
    NarrowedHCJ[i,"Days_in_Program"] <- difftime(as.POSIXct("2019-3-1", format = "%Y-%m-%d", tz = "") , NarrowedHCJ[i,"Dat_Initial_Assessment_was_Completed__c"], units="days")
  }
  else {
    NarrowedHCJ[i,"Days_in_Program"] <- NA
  }
}

TestNarrow <- NarrowedHCJ %>% filter(!is.na(NarrowedHCJ$Days_in_Program))# WINNER WINNER!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

TestNarrow <- TestNarrow %>% filter(TestNarrow$Days_in_Program > 0)
TestNarrow <- TestNarrow %>% filter(TestNarrow$Days_in_Program < 4000)

SpouseNHCJ <- TestNarrow %>% select(Id, Days_in_Program, Military_Spouse_Caregiver__c) %>% filter(Military_Spouse_Caregiver__c == 1)

mean(SpouseNHCJ$Days_in_Program)
#the average amount of days in the program for spouses is roughly 222 days.

#ggplot(TestNarrow, aes(x= Days_in_Program, y=Military_Spouse_Caregiver__c)) + geom_point()
# nah I thought a scatterplot would help but it didn't
```

Q: How does this differ from the average veteran client? 

```{r}

VeteranNHCJ <- TestNarrow %>% select(Id, Days_in_Program, Military_Spouse_Caregiver__c) %>% filter(Military_Spouse_Caregiver__c == 0)

mean(VeteranNHCJ$Days_in_Program)

# The average amount of days for a veteran client is roughly 266 days, which means on average a veteran will spend 44 more days in
# the program than a military spouse.

```

Q: What is the demographic profile of the military spouses who are registering (gender, location, service members status, level of education?)  

```{r}
SpouseDemographic <- Hire_Contact_Join[,c(1,4:6,25,50,108,123,184,321)] %>% filter(Military_Spouse_Caregiver__c == 1)
SpouseDemographic[SpouseDemographic == ""] <- NA

#Gender
SpouseDemographic <- SpouseDemographic[!is.na(SpouseDemographic$Gender__c),]
SpouseDemographic %>%
  group_by(Gender__c) %>% 
  summarise( percent = 100 * n() / nrow(SpouseDemographic))

#Location (reset each time)
SpouseDemographic <- Hire_Contact_Join[,c(1,4:6,25,50,108,123,184,321)] %>% filter(Military_Spouse_Caregiver__c == 1)
SpouseDemographic[SpouseDemographic == ""] <- NA

SpouseDemographic <- filter(SpouseDemographic, MailingState %in% c("AL","AK","AZ","AR","CA","CO","CT","DE","FL","GA","HI","ID","IL","IN","IA","KS","KY","LA","ME","MD","MA","MI","MN","MS","MO","MT","NE","NV","NH","NJ","NM","NY","NC","ND","OH","OK","OR","PA","RI","SC","SD","TN","TX","UT","VT","VA","WA","WV","WI","WY","DC", "PR"))


SpouseDemographic <- SpouseDemographic[!is.na(SpouseDemographic$MailingState),]
SpouseDemographic %>%
  group_by(MailingState) %>% 
  summarise( percent = 100 * n() / nrow(SpouseDemographic))

#Status
SpouseDemographic <- Hire_Contact_Join[,c(1,4:6,25,50,108,123,184,321)] %>% filter(Military_Spouse_Caregiver__c == 1)
SpouseDemographic[SpouseDemographic == ""] <- NA

SpouseDemographic <- SpouseDemographic[!is.na(SpouseDemographic$Service_Members_Status__c),]
SpouseDemographic %>%
  group_by(Service_Members_Status__c) %>% 
  summarise( percent = 100 * n() / nrow(SpouseDemographic))

#Education
SpouseDemographic <- Hire_Contact_Join[,c(1,4:6,25,50,108,123,184,321)] %>% filter(Military_Spouse_Caregiver__c == 1)
SpouseDemographic[SpouseDemographic == ""] <- NA

SpouseDemographic <- SpouseDemographic[!is.na(SpouseDemographic$Highest_Level_of_Education_Completed__c),]
SpouseDemographic %>%
  group_by(Highest_Level_of_Education_Completed__c) %>% 
  summarise( percent = 100 * n() / nrow(SpouseDemographic))


#After looking at our data our military spouses are primarily female (at a whopping 92%!), primarily in the United States especially in the states of California, Texas, and North Carolina. They are typically the spouse of a partner who is active duty, although a quarter of them are spouses of a veteran who is retired or separated from the military. Finally, their education seems to show about a third of them have received a bachelors and another third has received their GED, a bit surprising roughly 20% have a post graduate degree as well.
```

Q: How does their Service Members status affect their time to hired status? (Note Service Members status is a new field we have just started tracking.)

```{r}
UpdatedSpouseDemographic <- left_join(SpouseNHCJ, SpouseDemographic, by = c("Id"))

UpdatedSpouseDemographic <- UpdatedSpouseDemographic[,c(1,2,10)]

USD <- UpdatedSpouseDemographic %>% 
    mutate_all(~ifelse(. %in% c("N/A", "null", ""), NA, .)) %>% 
    na.omit()


summary(as.factor(USD$Service_Members_Status__c))

GraphData <- USD %>%
  group_by(Service_Members_Status__c) %>%
  summarise_at(vars(Days_in_Program), list(Average_Days_in_Program = mean))

ggplot(data = GraphData) + 
  geom_bar(mapping = aes(x = Service_Members_Status__c, y = Average_Days_in_Program, fill = Service_Members_Status__c), stat = "identity") + labs(x= "Status", y = "Avg Days in Program") + theme(legend.position="none")

# The average estimate of W-3, O-6, & E-1 seem to have the longest amount of time in the program compared to W-2, O-2 & O-5. What this means for the military spouses is that those who are in the program who are generally lower rank (E1 is the lowest rank in the military for Enlisted) will spend more time in the program. ...................... oh geeez it's status not rank gah well i wonder still why colonels wives are looking for jobs ugh let's try this again

# Military spouses who's partner is either retired or deceased take longer in the program than military spouses who's spouse is active duty or in the reserves.


```

Q: Is there a correlation between education level and the black rate for military spouses.  

```{r}

EducationBlackRate <- NarrowedHCJ[,c(1,2,3,8)]



#EducationBlackRate <- EducationBlackRate %>% filter(!is.na(EducationBlackRate$Date_Turned_Black__c))
#EducationBlackRate <- EducationBlackRate %>% mutate_all(na_if,"")

EducationBlackRate <- EducationBlackRate %>% 
    mutate_all(~ifelse(. %in% c("N/A", "null", ""), NA, .)) %>% 
    na.omit()

summary(as.factor(EducationBlackRate$Highest_Level_of_Education_Completed__c))

EducationBlackRate %>%
  group_by(Highest_Level_of_Education_Completed__c) %>%
  summarize(n())

EBRGD <- EducationBlackRate %>% filter(Military_Spouse_Caregiver__c == 1)

EBRGD <- filter(EBRGD, Highest_Level_of_Education_Completed__c %in% c("2 Year Degree (AA, AS, etc.)", "4 Year Degree (BA, BS, etc.)","High School/GED", "Post-Graduate Degree (MA, MS, JD, etc.)"))

EBRGD %>%
  group_by(Highest_Level_of_Education_Completed__c) %>%
  summarize(n())


ggplot(EBRGD, aes(Active_Color__c, ..count..)) + geom_bar(aes(fill = Highest_Level_of_Education_Completed__c), position = "dodge")

#now we have them all out in a pretty graph let's look at the percentage for just the black grounp

EBRGD   %>% 
 filter(complete.cases(Highest_Level_of_Education_Completed__c)) %>% 
  filter(Active_Color__c == "Black") %>%
 count(Active_Color__c, Highest_Level_of_Education_Completed__c) %>% 
 group_by(Active_Color__c) %>% 
 transmute(Highest_Level_of_Education_Completed__c, Percentage=n/sum(n)*100)

# Black	2 Year Degree (AA, AS, etc.)	16.37765		
# Black	4 Year Degree (BA, BS, etc.)	25.81888		
# Black	High School/GED	43.54528		
# Black	Post-Graduate Degree (MA, MS, JD, etc.)	14.25819	
# Yes there is a correlation, while it shows throughout all of the color rates, black shows a distinction
# where the majority of spousal that are in the Black category do not have any education past high school.

```

Q: What percentage of military spouse clients say that they are underemployed vs. unemployed? 

```{r}
EmployHCJ <- Hire_Contact_Join[,c(1,52,321)] %>% filter(Military_Spouse_Caregiver__c == 1)


EmployHCJ <- EmployHCJ %>%  mutate_all(~ifelse(. %in% c("N/A", "null", ""), NA, .)) %>% 
    na.omit()

EmployHCJ %>%
  group_by(Status__c) %>% 
  summarise( percent = 100 * n() / nrow(EmployHCJ))

# 54% say they are unemployed and 9% say they are under employed.
```

Q: How many spouses who registered for our services who say that they are underemployed turn blue vs grey? (Would like to see this data because military spouses tend to remain underemployed.)

```{r}
BlueVsGrey <- Hire_Contact_Join[,c(1,52,265, 321, 401)] %>% filter(Military_Spouse_Caregiver__c == 1)

BlueVsGrey <- BlueVsGrey %>% filter(Status__c == "Under employed - Insufficient income")

GBVG <- BlueVsGrey[,c(1,3)]

GBVG <- GBVG %>%  mutate_all(~ifelse(. %in% c("N/A", "null", ""), NA, .)) %>% 
    na.omit()


#109 turned grey

BBVG <- BlueVsGrey[,c(1,5)]
BBVG <- BBVG %>%  mutate_all(~ifelse(. %in% c("N/A", "null", ""), NA, .)) %>% 
    na.omit()
#115 were hired

# Of our 423 military spouses who claimed they were underemployed, 109 went to the grey status and 115 were hired and went to the blue status.

```

Q: Are a large percentage of military spouses who are overseas completing federal resume reviews?  

```{r}
# which( colnames(Hire_Contact_Join) == "Federal_Hire__c.y" )

OverseasResumeReviews <- Hire_Contact_Join[,c(1,6,136,206,321)] %>% filter(Military_Spouse_Caregiver__c == 1)

OverseasResumeReviews <- OverseasResumeReviews %>% filter(!MailingCountry  %in% c('United States', 'USA', 'Unites States'))

OverseasResumeReviews <- OverseasResumeReviews %>%  mutate_all(~ifelse(. %in% c("N/A", "null", ""), NA, .)) %>% 
    na.omit()

OverseasResumeReviews <- OverseasResumeReviews[,c(2,3,4)]


#Surprisingly no, none of military spouses are completing federal resume reviews.

```

Q: How many of those clients accept federal employment? 

```{r}
#Looking at the documentation above none of them have accepted federal employment.
```

Q: How many spouses vs veterans are taking part in our volunteer services (career counseling, mock interviews, etc.)

```{r}
Hire_Contact_Join <- left_join(SFContact, SFHI, by = c("Id" = "Client_Name__c"))
VolunteerServices <- Hire_Contact_Join[,c(1,321,200,202,203,204,206,207,208,210,211,212,214,215,216,217,229,230)]
VolunteerServices[is.na(VolunteerServices)] = 0

VSVeterans <- VolunteerServices %>% filter(Military_Spouse_Caregiver__c == 0)
VSSpouses <- VolunteerServices %>% filter(Military_Spouse_Caregiver__c == 1)


# VSVeterans %>%
#   group_by(MyTrak_Total_Questions_Answered__c) %>% 
#   summarise(NumPat=n(),prop=sum(treatment==1)/n())

# d %>% group_by(region) %>% summarize(NumPat=n(),prop=sum(treatment==1)/n())

summary(as.factor(Hire_Contact_Join$MyTrak_Mock_Interview_Request__c))
which( colnames(Hire_Contact_Join) == "MyTrak_Mock_Interview_Request__c" )

#VSVeterans$Means <- apply(VSVeterans,1,mean)

VSVeterans %>%
  group_by(MyTrak_Essentials_Complete__c) %>%
  summarize(n())

mean(VSVeterans$MyTrak_Essentials_Complete__c, na.rm = TRUE)

t.test(VSVeterans$MyTrak_Essentials_Complete__c, conf.level=0.05, alternative="two.sided")

#With 95% confidence 16.35%-16.36% of VSVeterans will do the MyTrak_Essentials_Complete


### Okay let's add a mean column, gotta get rid of the ID and Spouse ID

VSVeterans <- VSVeterans[,c(3,4,6,7,9:12)]
VSSpouses <- VSSpouses[,c(3,4,6,7,9:12)]

VSVeterans$Means <- apply(VSVeterans,1,mean)
VSSpouses$Means <- apply(VSSpouses,1,mean)

VSVeterans %>%
  group_by(Means) %>%
  summarize(n())

VSSpouses %>%
  group_by(Means) %>%
  summarize(n())

VSVeterans %>%
  group_by(Means) %>% 
  summarise( percent = 100 * n() / nrow(VSVeterans))

VSSpouses %>%
  group_by(Means) %>% 
  summarise( percent = 100 * n() / nrow(VSSpouses))

# First I utilized MyTrak to look into who is using the volunteer services, then I narrowed it into two categories of Veterans and Spouses. Of the 132,659 attached to MyTrak, 127,418 were veterans and 5,241 were spouses. But that still had people listed who had zero participation. From there I calculated the means off the binary values and saw that 77.49% of the veterans had zero participation and 53.29% of spouses had zero participation, calculated off of the reverse (22.51% of 127,418 & ) there are roughly 28,682 veteran participants and 2,448 military spouse participants. 

```

